\chapter{The Hosting Company}




\section{Talan Group}
Talan is a consulting company specializing in the integration of New Information and Communication Technologies in the field of customer relations. It focuses its sector expertise on service operators, namely Finance and Insurance, Telecoms and Media, Energy and Utilities, and Transport and Logistics.
\\
\\
Talan was founded in 2002 by Mehdi Houas, Eric Benamou, and Philippe Cassoulat. It delivers its business, functional and technological on an international scale with more than 1,000 employees, across New York, London, Hong Kong, Paris, and Montreal. To accelerate its development, Talan opened a nearshore development center in Tunisia called "Talan Tunisia International", mobilizing to date around 180 new technology development engineers that are constantly working with major international clients.
\\

\section{Activity Sectors}
Talan basically covers:
\begin{itemize}
    \item The finance sector through collaboration with investment banks and insurance companies.
    \item The telecommunications sector through projects aimed at telecom operators and a set of internet service providers.
    \item The transport and logistics sector.
    \item The energy sector by developing projects for utility operators (electricity, gas, water, etc.).
\end{itemize}
These different sectors are characterized by the provision of a set of services:
\begin{itemize}
    \item Advice and assistance to project management.
    \item Redesign and optimization of business processes.
    \item Support for major transformation projects.
    \item Alignment of information systems to organizational changes and change management.
\end{itemize}

\section{Contacts}
\textbf{Talan Tunisia} \\
Address: 10 Rue de l’énergie solaire – Impasse N°1 Charguia 1, 
Tunis 2035 \\
Tél. : +216 7001 5010 \\
Fax : +216 7001 5007 \\

missing: 
? turnover, organization chart, certifications \\
acquired, the staff ratio… 
