\chapter{Introduction}


\indent Due to the pandemic that started in 2020, many companies has put initiations to limit the consequences, and basically started re-imaging the current world with the new technologies that evolved over the years. There's no doubt that Artificial Intelligence, Blockchain, 5G, Internet of Things.. all have came to solve as much problems that the human race encounters as  possible, and we all agree that it is time to put them into test to fight this new world crisis. 
\bigskip

\indent Meta,  previously known as Facebook, were the first to market a new product, the \textit{Horizon Worlds}, which is a Virtual Reality Powered world of Avatars, to be a digital way to \textbf{Do things}. This \textit{Metaverse} as people started calling this movement, is being proposed as a solution to transfer everything that's can be done remotely to a more \textit{Alive} version. An Example of a use case is what \textbf{Talan Inc.} developed as a Digital World, or a "Metaverse", where you can work, schedule meetings, and Live a professional work day at Talan like it was used to be, without loosing the real life events and features, or maybe enhancing them.
\bigskip

\indent With the rise of this technology, a lot of challenges were introduced, like Scaling, Security, Privacy etc.. So technologies like Blockchain, 5G, Artificial Intelligence were a great enhancers of a lot of Metaverse platforms.
\bigskip

\indent In this context, Talan Innovation Factory decided to jump to this trend, and use it as a technology base for the 2022'th edition of \textit{SummerCamp}, a yearly internship program were interns are asked to develop a solution from a theme that's announced at the beginning using innovative technology, and deliver an MVP (\textit{Minimum Viable Product}) at the end. The theme this year was Sports and its presence in the new Metaverse era.  

\section{Scenario}
Given a digital world, where people have their own customized avatars, and with the ability to attend real life matches, museums, shops... How are we going to maintain the integrity and bring the control into the hands of users? and within this context how can we administer this world with keeping the fact that the user is the owner of his rights and actions just like the real world is like, under the digital justice? How can we just convince the users that this world and the money that they are paying inside is not a scam? And more than that how can we use all those facts to attract them to exist in our world?

\section{Solution}
The proposed solution, was developing a decentralized layer of control to administer the critical parts of the metaverse. Initially we have developed 3 key components, each with a certain responsibility, which are:
\bigskip

- \textbf{Ticketing Marketplace}:  A place where you can buy digital tickets to attend Sporting Events, that's going to be streamed in the metaverse. A buyer can resell his ticket before the match with the same price, or with a custom price after the match as a collectible.
\bigskip

- \textbf{Decentralized Identity}: Since each visitor will have his own avatar and name, and anything else that will be assigned to his identity, A digital identity should be assigned to him, with the focus on ownership and the control that's only granted to the owner of the identity and whoever the owner grants them the rights to alter any metadata, like the component that will assign him an avatar.
\bigskip

- \textbf{Streaming Rights Campaigns | Featuring DAOs}: To make the users feel the importance and have the right to contribute to their new home, hopefully, anyone can start a campaign to bring the streaming rights of his favorite sport event, like the Champions League, Wimbledon Championships, or anything to the metaverse. Anyone can be part of this initiatives and by buying an amount of equity that will represent the voting weight of any decision that's going to be proposed inside this organization, Every member is a decider for the future of the event inside the metaverse and the vote will definitely be taken in consideration without a third party. 

\section{Definitions}
To make sure you, the reader, aware with what we are solving and proposing, here is few definitions that will put you on track:
\subsection{Blockchain}
A blockchain is a digital ledger of all cryptocurrency transactions. It is constantly growing as "completed" blocks are added to it with a new set of recordings. Each block contains a cryptographic hash of the previous block, a timestamp, and transaction data. Bitcoin nodes use the block chain to differentiate legitimate Bitcoin transactions from attempts to re-spend coins that have already been spent elsewhere.
There are a few key reasons why blockchain technology is so useful.
\textit{First}, it is incredibly secure. The data is encrypted and each transaction is linked to a unique digital signature. This makes it difficult for anyone to tamper with the data. \textit{Second}, blockchain is transparent. All transactions are visible to everyone on the network. This makes it easy to track and verify data. \textit{Third}, blockchain is decentralized. There is no central authority controlling the data. Instead, it is distributed across a network of computers. This makes it resistant to tampering or interference.

\subsection{Smart Contracts}
Smart contracts are self-executing contracts with the terms of the agreement between buyer and seller being directly written into lines of code. This code is deployed onto the Ethereum blockchain and runs exactly as programmed without any possibility of fraud or third party interference.

\subsection{Ethereum, Polygon, Solana}
\textbf{Ethereum} is a decentralized platform that runs smart contracts: applications that run exactly as programmed without any possibility of fraud or third party interference.
\textbf{Solana} is a high-performance decentralized finance (DeFi) platform built on a Proof-of-Stake (PoS) blockchain. \textbf{Polygon} is a protocol and framework for building and connecting Ethereum-compatible blockchain networks.

\subsection{Non-Fungible Tokens | NFT}
NFTs are non-fungible tokens. They are digital assets that are unique and cannot be replaced. NFTs are often used to represent items in video games, art, and other digital media.

\subsection{Decentralized Identity}
A decentralized identity is an online identity that is not controlled by a central authority. Instead, it is stored on a decentralized network. This makes it resistant to tampering or interference.

\subsection{Decentralized Autonomous Organization | DAO}
A DAO is a decentralized autonomous organization. It is an organization that is run by a set of rules encoded on the Ethereum blockchain. DAOs are transparent and resistant to fraud or interference.




